Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2013-10-07 tex/paper1/paper1.tex
added in a white-red noise comparison plot, and included it in the paper

\section{Floating material and so forth}

@@

\begin{figure}
\epsscale{.80}
\plotone{f1.eps}
\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
\end{figure}

>>>>

\section{Coronal seismology and the effect of background assumptions}
\label{sec:corseis}

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a power spectrum $P(f)\tilde\mbox{frequency^{-1.77}}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet power spectrum for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.}\label{fig:comparison}}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\tilde\mbox{frequency^{-1.77}}$ with no explicit
oscillatory content, following the construction procedure of
\cite{vaughan2010}.  Figure \ref{fig:comparison}(b) shows that the
assumption of a white-noise background and a 95\% confidence level
leads to the positive detection of significant oscillatory power in
this time series. Figure \ref{fig:comparison}(c) shows that the
assumption of a red-noise background with the same confidence level
significantly reduces the area for which a detection may be claimed.
Raising the confidence level to 99\% or higher

@@
